Summary Tables

### 2020-02-20 summary_tables.Rmd
Use qualified name for a function (n), and comment out PA calculations

  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

@@

## Physical activity tables
Case study specific physical activity tables for backgound (non-travel) PA, and baseline and five scenarios (non-travel + travel)

```{r mmets = "asis"}

for(city in cities){
  df1 <- as.data.frame(io[[city]]$synth_pop$work_ltpa_marg_met)
  colnames(df1) <- "mmet"

  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df1) * 100, 1))

  td2 <- df1 %>%
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))

  td3 <- cbind(td1, td2)
  td3 <- as.data.frame(t(td3))

  df2 <- select(io[[city]]$outcomes$mmets, base_mmet : scen5_mmet)

  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df2) * 100, 1))

  td5 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    group_by(scenario) %>% 
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))

  td6 <- left_join(td4, td5, "scenario")
  td6 <- as.data.frame(t(td6))
  td6 <- td6[-1,]
  td6 <- mutate_all(td6, function(x) as.numeric(as.character(x)))

  td <- cbind(td3, td6)

  colnames(td)[1] <- "Background (non-travel)"
  colnames(td)[2] <- "Baseline"
  colnames(td)[3:7] <- rownames(scen_prop)

  print(kable(td, caption = paste("Marginal MET-h/wk for ", city)))
  cat("\n")
}

```{r pa, echo = F, message = F}

if (plot_mmets){

  dfSummary(accra_mmets <- io[["accra"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(sao_paulo_mmets <- io[["sao_paulo"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(delhi_mmets <- io[["delhi"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(bangalore_mmets <- io[["bangalore"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
}

>>>>

  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = dplyr::n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

@@
